Visualizations for the manuscript

### 2022-05-11 metanalysis_visualization/manuscript_Figures.Rmd
add forest plot with the meta package, adding the function to format it for JAMA

>>>>

## Forest plot meta library

### By site
```{r}
m.siteid <- metagen(TE = observed,
                 seTE = var_boot,
                 data = trends_siteid,
                 studlab = plotsLabel,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

summary(m.siteid)

forest.meta(m.siteid, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("Country"))

forest.meta(m.siteid, layout = "JAMA")
```

### By country
```{r}
m.country <- metagen(TE = pred,
                 seTE = se**2,
                 data = trends_country,
                 studlab = country,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

summary(m.country)

forest.meta(m.country, 
            sortvar = TE,
            print.tau2 = FALSE,
            leftlabs = c("Country"))

forest.meta(m.country, layout = "JAMA")
```
